\section{Introduction}

\epigraph{The questions run too deep\\
For such a simple man\\
Won't you please, \\
Please tell me what we've learned?}{Supertramp, \textit{The Logical Song}}

Supermassive black holes have nonzero supermass, the quantity that couples to $\mathcal{N}=1$ supergravity, while in theories with more supercharges one may have superdupermassive black holes, and so on.
Just as the no-hair theorem tells us that non-rotating black holes can be described as massive and charged, the no-hair supertheorem tell us that non-rotating superheavy black holes can be described as supermassive and supercharged.
String theory provides hope to understand how to go beyond the semiclassical limit to describe in detail if and how black holes preserve unitarity, while superstring theory provides hope to understand the unitarity of supermassive black holes.

With the recent observation of normal black hole \cite{Abbott:2016blz,Abbott:2016nmj,Abbott:2017vtc,Abbott:2017oio,Abbott:2017gyy} and neutron star\cite{TheLIGOScientific:2017qsa} mergers via gravitational waves by the super-sensitive Advanced LIGO and VIRGO detectors, it is not unreasonable to expect gravitational-wave detections of supernovae of collapsing superstars or violent supermassive black hole astrophysical phenomena are on the horizon or, if you'll forgive the absurd pun, superhorizon. 
Indeed, the superposition of the gravitational-wave signals can be approximated as a stochastic background, just as the superimposition of all of the gravitational-wave academic publications impact the scholastic background.

The potential discovery space of astrophysical observation seems to supersede that of direct detection methods. 
Direct detection of superpartners of familiar particles, with nonzero supermass, was a potential discovery at the Superconducting Super Collider, superior to the LHC due to its souped-up center-of-mass and supercenter-of-supermass collision energy, partly due to the stupefying radius of its hoop.
When the super-expensive Superconducting Super Collider was superseded in the Congressional budget by the International Superspace Superstation, physicists' superegos were superficially bruised and a superb opportunity to supersize our superintelligence was lost.\footnote{Other supervenient inventions were no doubt lost as well.
With CERN as a guiding historical precedent, had the Superconducting Super Collider not been deemed superfluous we might have, by now, cruised our supercars down the Information Superduperhighway.}
Other direct-detection experiments such as Super-Kamiokande have successfully performed as real-time supernova monitors and detected associated neutrinos, but, unfortunately, no sneutrinos, which are expected in the Standard Supermodel.\footnote{SuperK is a Cherenkov detector consisting of about 13,000 PMTs mounted inside a superstructure of 50 kilotons, or about half a Panamax supertanker, of ultrapure water.  The PMTs are arranged in $3\times4$ arrays termed `supermodules' \cite{Fukuda:2002uc}.
SuperK also takes advantage of `Super Control Headers', a `Super-Low Energy trigger', and a `Super Memory Partner Module' to aid its search.
} We note that, although the definition of the Standard Supermodel has historically been time dependent, it has always been derived from superficial characteristics (thereby suppressing the full degree of human diversity) and generally reinforces rather than challenges the status quo \cite{fashionmodels}.


While astronomical observations of supergiants or of the supermoon are likely irrelevant, balloon experiments which monitor cosmic rays and hunt for their astrophysical origins such as SuperTIGER\cite{Binns:2014xpa} may also shed light on these phenomena.
Supertranslations of superpositions of supersymmetric supermassive black holes in minisuperspace might accrete supernova remnant winds at a super-Eddington rate via the superradiance instability; associated violent episodes should produce clear signatures.

Another superpotential avenue of discovery is super-low-energy spectroscopy.
Supersoldiering on beyond fine and hyperfine splittings, spectroscopic detections of superfine splittings may provide an opportunity for \st{ultra-} super-low energy precision experiments to snoop on the small shifts associated with otherwise virtually-unobservable virtual superpartner loops.
Another sensitive probe to supernal effects is the neutron lifetime, with recent improvements in sensitivity by UCNA, using a superratio analysis \cite{Brown:2017mhw}, and P\textsc{erkeo} III, with its supermirror guide\cite{Markisch:2018ndu}.

Henceforth, when we need to distinguish between mass and supermass we henceforth use the `super' superscript, $m^{\text{super}}$.  When referring to the supermass of a subsystem we use the `sub' subscript, $m^{\text{super}}_{\text{sub}}$.  This avoids a disastrous notation with `sub' superscripts and `super' subscripts.
